\documentclass[10pt,a4paper]{article}
\author{Huang Teng-Hui}
\title{Documentation}
\begin{document}
\section{Environment}
We recommend Linux platform to run this program, source file are written in C,however C++ compiler is also needed to run other programs.
\section{Makefile}
For simplicity, type "make" at main directory, then enter "sh train.sh" to run structured SVM.
Detailed makefile command are listed as follows, you can also check Makefile yourself!:
\subsubsection*{all:}
 compile structured SVM programs and some useful programs preparing SVM features.
\subsubsection*{structSvm:}
 compile structured SVM api program.
\subsubsection*{svmGen:}
 merge features and labels together. 
\subsubsection*{featNorm:}
 normalize features to zero mean, unit variance.
\subsubsection*{svmTrim:}
 trimming predicted label sequence.
\subsubsection*{makeFrameData:}
 splice features to take frame sequence into account.
\subsubsection*{clean:}
 remove objects and executables
\section{Files \& Directories}
This is a modified version from a package source, so we only list the files which are the essence for this program.  
\subsection{Directories}
\subsubsection*{svm\_ struct:}
Contains structured SVM api source files.
\subsubsection*{example:}
All source files related to features are in this directory.
\subsubsection*{bin:}
Compiled executables are in this directory.
\subsubsection*{model:}
Structured SVM model directory, weight sequence of psi dimensions, build automatically while compiling this program

\subsection{Source files}
\subsubsection*{svm\_struct/src/svm\_struct\_api.c:}
The api interface, this is the main work for HW2, for example, find\_most\_violated\_constraint, psi function, etc.
\subsubsection*{svm\_struct/include/svm\_struct\_api\_type.h:}
Most struct definition are written in this file.
\subsection{Script files}
We prepared some shell scripts for you to run this program easily, you can modify parameters in these scripts to do any experiment you want.
\subsubsection*{train.sh:}
Type "sh train.sh" then it will begin to train structured SVM model, if features path are given correctly.
\subsubsection*{test.sh:}
Type "sh test.sh" to classify testing feature, then the result of this will be trimmed.
\subsubsection*{svmValGen.sh:}
This script will segment you training faeture file into training set and validating set.
\subsubsection*{makeFrameData.sh:}
Splice originial feature, takes previous and later frames into account.

\end{document}
